
% Copyright © 2008-2010 Tom Adams
%
% Permission to use, copy, modify, and/or distribute this software for any
% purpose with or without fee is hereby granted, provided that the above
% copyright notice and this permission notice appear in all copies.
%
% THE SOFTWARE IS PROVIDED "AS IS" AND THE AUTHOR DISCLAIMS ALL WARRANTIES WITH
% REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED WARRANTIES OF MERCHANTABILITY
% AND FITNESS. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY SPECIAL, DIRECT,
% INDIRECT, OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM
% LOSS OF USE, DATA OR PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE OR
% OTHER TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR
% PERFORMANCE OF THIS SOFTWARE.

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{supertabular}
\usepackage[top=2cm, bottom=2cm, left=3cm, right=3cm]{geometry}

% Header and footer
\usepackage{lastpage}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{}
\cfoot{\me{} -- \thepage/\pageref{LastPage}}

% Allow for the easy creation of a privacy-maintaining CV
\newcommand{\secret}[1]{\textit{---Withheld---}}
\renewcommand{\secret}[1]{#1}

% Helpful commands
\newcommand{\iri}[1]{\url{#1}}
\newcommand{\tabsection}[1]{\ {\kern 0em \textit{\textbf{#1}}}}
\newcommand{\org}[1]{\textit{#1}}
\newcommand{\pagew}{5.9in}
% Following line from http://www.cse.wustl.edu/~mgeorg/html/tildalatex.html
\newcommand{\urltilda}{{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}}

% Information
\newcommand{\me}{Tom Adams}
\newcommand{\thetitle}{Curriculum Vitæ}
\newcommand{\phone}{\secret{(+44) 1337}}
\newcommand{\email}{\iri{tomadams@holizz.com}}
\newcommand{\address}{
  \secret{111 Foobar Lane}\\
  London\\
  United Kingdom\\
  \secret{A11 1AA}}

\input{secret.tex}

\title{\thetitle}
\author{\me}

% Pretty title
\renewcommand{\maketitle}{
  \begin{center}
    \begin{tabular}{lr}
      \parbox{2in}{
        {\Huge \me}
        \par\rule{0pt}{0pt}\par
                 {\Large \thetitle}
      }
      &
      \parbox{2in}{
        \begin{flushright}
          \address\\\ \\
          \phone\\
          \email
        \end{flushright}
      }
    \end{tabular}
  \end{center}
}

% 1. No numbered sections
\setcounter{secnumdepth}{0}

\begin{document}

\maketitle

\section{Employment}
\newcommand{\ecolw}{2.9in}
\tablefirsthead{\textbf{Organisation} & \textbf{Role} & \textbf{Date}\\\hline}
\tablelasttail{\\\hline}
\tablehead{}
\tabletail{}
\begin{supertabular}{p{\ecolw}ll}
\\New Roots, 347 Glossop Road, Sheffield, S10 2HP, Tel: 0114 272 1971 & Shop work, voluntary & June 2008 onward\\
\multicolumn{3}{p{\pagew}}{Responsibilities include: serving customers, cashing-up, answering the phone, packaging goods, stacking shelves.}\\\\
\hline\\

Childminding Network, South Square, Thornton, Bradford, BD13 3LD, Tel: 01274 435288 & Temporary office work & 2004\\\\
\hline\\

South Square Centre, South Square, Thornton, Bradford, BD13 3LD, Tel: 01274 834747 & Webmaster, voluntary & 2003/4\\\\
\hline\\

Hayton \& Associates, Thornton & One-off Web programming & 2004\\
\multicolumn{3}{p{\pagew}}{Wrote a simple \urltilda{}30 line Python script to email the contents of a submitted form.}\\

%Alphabet Zoo, Girlington, Bradford & Staff & 2004
\end{supertabular}

% Important things employers will be interested in
\section{Other}
\begin{itemize}
\item Attended PyConUK 2007, PyConUK 2008, and EuroPython 2009.
\item A contributor to several Free Software projects (\iri{http://holizz.com/portfolio})
  \begin{itemize}
  \item Filing bug reports.
  \item Writing patches to fix bugs or add new features.
  \item Writing libraries and applications and releasing them under a Free licence.
  \end{itemize}
\item Treasurer of University of Sheffield's Capoeira society 2008/9
  \begin{itemize}
  \item Handled payments to the class' instructor and charities, also taught a class once.
  \end{itemize}
\item Course representative at University of Bradford 2006/7
  \begin{itemize}
  \item Acted as a relay between coursemates and staff, attended Student--Staff Liaison Committee meetings on a weekly basis.
  \end{itemize}
\item President of University of Bradford's Cult TV and Anime society 2006/7 (and member of the committee 2005/6)
  \begin{itemize}
  \item Responsible for booking rooms, procuring audio/visual equipment, marketing.
  \end{itemize}
\end{itemize}

\break

\section{Qualifications}
\newcommand{\colw}{3.9in}
\tablefirsthead{
  & \textbf{Qualification} & \textbf{Result} & \textbf{Graduated}\\\hline}
\tablelasttail{\\\hline}
\tablehead{}
\tabletail{}
\begin{supertabular}{p{0.1in}p{\colw}cr}

%\tabsection{Ongoing}\\

%\tabsection{Completed}\\

\\\Large$\star$&\parbox{\colw}{Postgraduate-Certificate Human Language Technology\\\org{University of Sheffield}}
& & \parbox{1in}{\begin{flushright}September 2007\\-- March 2009\end{flushright}}\\

\\&\parbox{\colw}{Japanese Language Skills level 3\\\org{Bradford College}}
& & August 2007\\

\\&\parbox{\colw}{Japanese Language Skills level 2\\\org{Bradford College}}
& & August 2007\\

\\\Large$\star$&\parbox{\colw}{BSc Computer Science Hons.\\\org{University of Bradford}}
& 2:1 & July 2007\\

\\&\parbox{\colw}{Japanese Language Skills level 1\\\org{Bradford College}}
& & May 2006\\

% UCAS points: 140
\\$\star$&A-Level Physics & D & 2004\\
$\star$&A-Level Psychology & E & 2004\\
$\star$&AS Mathematics & C & 2003\\
$\star$&AS Sociology & U & 2004\\
&\org{Thornton Grammar School}\\

\\&\parbox{\colw}{Introduction to Mendhi/Henna Skin Decoration\\
\org{Bradford College}}
& & 2004\\

\\&\parbox{\colw}{Take 5 for Play\\\org{Bradford Area Play Association}}
& & 2003\\

\\$\star$&\parbox{\colw}{10 GCSEs including As in Maths and Double Science, Cs in English and German\\
\org{Thornton Grammar School}}
& & 2002\\

\\&\parbox{\colw}{Coding and Programming in C level 2 (City \& Guilds)\\
\org{Bradford College}}
& & 2001\\

\end{supertabular}

\section{References}
\newcommand{\rcolw}{3in}
\tablefirsthead{}
\tablelasttail{}
\tablehead{}
\tabletail{}
\begin{supertabular}{p{\rcolw}p{\rcolw}}
\parbox{\rcolw}{
Harry Metcalfe\\
Managing Director of The Dextrous Web\\
Tel: (+44) 020 7940 4780\\
The Dextrous Web\\
11 Marshalsea Road\\
London\\
SE1 1EN\\
United Kingdom
} &
\parbox{\rcolw}{
Grace Vincent\\
Tel: (+44) 0114 2721971\\
New Roots\\
347 Glossop Road\\
Sheffield\\
South Yorkshire\\
S10 2HP\\
United Kingdom
}
\end{supertabular}

\end{document}
